Effect of metabolic state on \textit{Paraclostridium bifermentans} surface properties and the implications for lead removal

### 2021-10-25 Writeup/Catalysts/MDPI_template/template.tex
Added discussion on dead vs liv

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, and has been shown to remove up to 93~\% of Pb(II) from solution \cite{Brink2017} by precipitating it out as PbS and Pb(0) \cite{Brink2020}. Following kinetic studies on the consortium, H\"orstmann et al. \cite{Horstmann2020c} proposed a two-phase exponential decay model to describe Pb(II) removal and attributed an initial rapid phase to adsorption. Subsequent research built on this proposal by demonstrating that significant Pb(II) removal with the consortium took place following sterilization with NaN\textsubscript{3} \cite{VanVeenhuyzen2021}, highlighting the involvement of adsorption as a rather than the metabolically dependent precipitation.

@@

@@

The chemical composition of bacteria surfaces for both Gram-positive and Gram-negative bacteria are rich in negatively charged functional groups that result in an overall negative surface charge and facilitate the attraction of positively charged metal cations like ionic lead \cite{Vijayaraghavan2008}. These functional groups also allow for chemisorption to take place, where hydrogen ions are exchanged for Pb(II)
ions \cite{Lu2012}.
Chemisorption not only prevents lead from entering cells, but 
Functional
group complexation can be a prominent adsorption mechanism for some bacteria
that use it to concentrate terminal electron accepting ions on the cell wall surface

>>>>

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, and has been shown to remove up to 93~\% of Pb(II) from solution \cite{Brink2017} by precipitating it out as PbS and Pb(0) \cite{Brink2020}. Following kinetic studies on the consortium, H\"orstmann et al. \cite{Horstmann2020c} proposed a two-phase exponential decay model to describe Pb(II) removal and attributed an initial rapid phase to adsorption. Subsequent research investigated this attribution by demonstrating that significant Pb(II) removal with the consortium took place following sterilization with NaN\textsubscript{3} \cite{VanVeenhuyzen2021}, highlighting the involvement of adsorption as a rather than the metabolically dependent precipitation.

@@

Significant adsorption of Pb(II) onto bacteria has been widely reported on Gram-positive genera such as \textit{Bacillus} \cite{Tunali2006,Ren2015,Salehizadeh2003} and \textit{Rhodococcus} \cite{Hu2020}, as well as Gram-negative genera like  \textit{Enterobacter} \cite{Lu2006,Ayangbenro2017} and \textit{Pseudomonas} \cite{Huang2013,Lin2006a,Chang1997,Uslu2006}. The chemical composition of bacteria surfaces for both Gram-positive and Gram-negative bacteria are rich in negatively charged functional groups that result in an overall negative surface charge and facilitate the attraction of positively charged metal cations like Pb(II) \cite{Vijayaraghavan2008}.

Several authors have noted that heavy metal onto living bacteria is noteably lower than on living
\cite{Hu2020,Mera1992,Johnson2007a}

These functional groups also allow for chemisorption to take place, where hydrogen ions are exchanged for Pb(II)
ions \cite{Lu2012}.

@@

Chemisorption not only prevents lead from entering cells, but 
Functional
group complexation can be a prominent adsorption mechanism for some bacteria
that use it to concentrate terminal electron accepting ions on the cell wall surface
